---
title: "Project2"
author: "Saipraveen Vabbilisetty(sxv165130), Manohar Katam(mxk164930)"
date: "November 25, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading all the libraries needed
```{r}
library(xts)
library(zoo)
library(lubridate)
library(forecast)
library(qdap)
library(dplyr)
library(anytime)
library(psych)
library(corrplot)
library(PerformanceAnalytics)
library(ggplot2)
```

# Reading Token Data and transforming it into Data frame
```{r}
setwd("C:\\Users\\praveen94\\Desktop\\Stats_Project\\Ethereum token graphs")
input_data <- read.delim('networkbnbTX.txt',sep = ' ',header = FALSE)
names(input_data)<- c("From_Node","To_Node","Unix_Time","Transaction_Amount")
input_df<- as.data.frame(input_data,na.rm=TRUE)
head(input_df)
```

# Dropping From Node and To Node as they are something like IDs and does not contribute to prediction
# Removing outliers if any
```{r}
drops <- c("From_Node","To_Node")
input_df<- input_df[ , !(names(input_df) %in% drops)]
input_df$Unix_Time <- as.Date(as.POSIXct(as.numeric(input_df$Unix_Time), origin = '1970-01-01', tz = 'UTC'))
multiplier<-10**18
input_df$Transaction_Amount<-input_df$Transaction_Amount/multiplier
head(input_df)
```
# Reading Price Data
```{r}
price_data <- read.delim('binance.txt',sep = '\t',header = FALSE)
names(price_data)<- c("Date","Open","High","Low","Close","Volume","MarketCap")
price_df <- as.data.frame(price_data, na.rm=TRUE)
price_df$Date <- as.Date(price_df$Date, "%B %d,%Y")
head(price_df)
```
# Extracting Number of Transactions feature
```{r}
filter1_df = as.data.frame(plyr::count(anydate(input_df$Unix_Time)))
names(filter1_df)<-c('Date','Num_Transactions')
head(filter1_df)
```
# Combining token and price data and Adding Lag Features
```{r}
combined_df1 <- inner_join(filter1_df,price_df,by=c('Date'))
combined_df1$Lag1 <- lag(combined_df1$Close, 1)
combined_df1$Lag2<- lag(combined_df1$Close, 2)
combined_df1<-na.omit(combined_df1)
head(combined_df1)

```
# Correlation plot
```{r}
correlation_df<-data.frame(combined_df1$Num_Transactions,combined_df1$Open,combined_df1$High,combined_df1$Low,combined_df1$Lag1,combined_df1$Lag2,combined_df1$Close)
correlation_df<-na.omit(correlation_df)
head(correlation_df)
```

```{r}
pairs.panels(correlation_df[1:7], hist.col="white", scale=TRUE)
chart.Correlation(correlation_df[1:7])
x <- cor(correlation_df[1:7],use = "na.or.complete")
corrplot(x, type="upper", order="hclust")
```
# Training features with complete data
```{r}
training_features<-data.frame(combined_df1$Open,combined_df1$High,combined_df1$Lag1,combined_df1$Lag2,combined_df1$Close,combined_df1$Date)
colnames(training_features)<-c('Open','High','Lag1','Lag2','Close','Date')
head(training_features)
```
# Auto correlation plot to see correlation between Lag Feature with Closing price
```{r}
acf <- acf(ts(training_features$Close), plot = FALSE, na.action = na.pass)
acf.plot <- with(acf, data.frame(lag, acf))
ggplot(data = acf.plot, mapping = aes(x = lag, y = acf)) +
  geom_hline(aes(yintercept = 0)) +
  geom_segment(mapping = aes(xend = lag, yend = 0))
```
# Separating out Training and Test Data (80 and 20 percents)
```{r}
training_data<- training_features[1:round(nrow(training_features)*0.8),]
testing_data<- training_features[round(nrow(training_features)*0.8):nrow(training_features),]
```
# Fitting the multiple linear regression model on training data
```{r}
fit <- lm(Close~Lag1+Lag2+Open, data=training_data)
summary(fit)
```
# Applying the training model to test data to get the predictions
```{r}
actual_values<-testing_data$Close
testing_data$predictions<-predict(object = fit,newdata=testing_data)

```
# Calculating RMSE error of Actual and Predicted Closing Price
```{r}
rmse <- function(error)
{
    sqrt(mean(error^2))
}
error <- actual_values - testing_data$predictions
rmse(error)
```
# Actual vs Predicted plot
```{r}
ggplot() + 
  geom_line(data = testing_data, aes(x = Date , y = Close, color = "red")) +
  geom_line(data = testing_data, aes(x = Date, y = predictions, color = "blue")) +
  xlab("Date") + ylab("Closing Price") + ggtitle("Binance Price Prediction") +
  scale_colour_discrete(name = "Legend", labels = c("Actual", "Predicted"))
```
